Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-05 paper_jasa.tex
outlining pieces that need to be updated

For all the three experiments, each subject saw a lineup just once. This doesn't allow fitting a lineup random effect, in addition to a subject random effect, but it does simplify the model since $\tau_{\ell i} = \tau_i$. The subject-specific probability ($p_i$) of successful evaluation of a lineup is then estimated using Equation \ref{eqn:mixed_power}. For computation we use R \citep{R} package lme4.

Table \ref{tbl:model_par} shows the parameter estimates of the mixed effects model of the subject-specific variation.

@@

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, sd=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, sd=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices. \cite{*** yifan's CC needs to be made into a tech report, and referenced here.}
Lineups chosen for the follow up eye-tracker experiment were (experiment 1) (1) $n=100, \beta=3, \sigma=5$, rep=1 (2) $n=100, \beta=5, \sigma=5$, rep=1 (3) $n=100, \beta=10, \sigma=12$, rep=1 and (4) $n=300, \beta=5, \sigma=5$, rep=1, and  (experiment 2) (5) $n=100, \beta=3.5, \sigma=12$, rep=1 (6) $n=100, \beta=4.5, \sigma=12$, rep=2 (7) $n=300, \beta=1, \sigma=5$, rep=1 and (8) $n=300, \beta=1, \sigma=5$, rep=2.

Experiment 3 does not have $p$-values associated with each plot, so the assumption can only be tested with the first two experiments. Practically, this is not an assumption that is explicitly made, because there will not be a $p$-value available. Rather it is assumed that the subject has the ability to select the plot with the most extreme structure. A few of the lineups indicated that occasionally people cue on different patterns, for example, in experiment 1 the lineup $\beta=0, n=100, sd=5, rep=1$ (first row, fourth column) many subjects chose the same plot, that had a higher $p$-value. Some of these anomalous lineups were selected for follow-up studies using an eye-tracker to investigate what people were looking at.

@@

@@

This work was funded by National Science Foundation grant DMS 1007697.

>>>>

For all the three experiments, each subject saw a lineup just once. This doesn't allow fitting a lineup random effect, in addition to a subject random effect, but it does simplify the model since $\tau_{\ell i} = \tau_i$. The subject-specific probability ($p_i$) of successful evaluation of a lineup is then estimated using Equation \ref{eqn:mixed_power}. For computation we use R \citep{R} package lme4 \citep{who are the authors of this package?}.

Table \ref{tbl:model_par} shows the parameter estimates of the mixed effects model of the subject-specific variation.  \green{What do we learn about the models from these parameter estimates? Explain this here too.}

@@

There are some noticeable exceptions to this rule. In experiment 1, when $\beta=5, n=300, \sigma=12, rep=3$, people tended to pick the plot with the second smallest $p$-value.  Same experiment, when $\beta=0, n=100, \sigma=5, rep=1$ people overwhelming chose a plot with much larger $p$-value. For several of these exceptions, along with several easy lineups, we followed up with a new experiment using an eye-tracker to examine what the observers were looking at in making their choices \citep{zhao2012}.
(Lineups chosen for the eye-tracker experiment were in experiment 1, (1) $n=100, \beta=3, \sigma=5, rep=1$ (2) $n=100, \beta=5, \sigma=5, rep=1$ (3) $n=100, \beta=10, \sigma=12, rep=1$ and (4) $n=300, \beta=5, \sigma=5, rep=1$, and in experiment 2, (5) $n=100, \beta=3.5, \sigma=12, rep=1$ (6) $n=100, \beta=4.5, \sigma=12, rep=2$ (7) $n=300, \beta=1, \sigma=5, rep=1$ and (8) $n=300, \beta=1, \sigma=5, rep=2$.)

Experiment 3 does not have $p$-values associated with each plot, so the assumption can only be tested with the first two experiments. Practically, this is not an assumption that is explicitly made, because there will not be a $p$-value available. Rather it is assumed that the subject has the ability to select the plot with the most extreme structure. A few of the lineups indicated that occasionally people cue on different patterns, for example, in experiment 1 the lineup $\beta=0, n=100, \sigma=5, rep=1$ (first row, fourth column) many subjects chose the same plot, that had a higher $p$-value. Some of these anomalous lineups were selected for follow-up studies using an eye-tracker to investigate what people were looking at.

@@

\green{
\begin{itemize} \itemsep 0in
\item Summarize the key pieces of the paper again, especially the major findings
\item Explain caveats, nuances, advantages with the work
\item Describe the next steps of the work, and possible ideas for future extensions
\end{itemize}
}

@@

This work was funded in part by National Science Foundation grant DMS 1007697.
